History of Social Work Research

### 2015-02-05 dataCleaning.Rmd
Major cleaning.

---
title: "History of Social Work Research"
author: "Summary of Data Cleaning Procedures"
output: html_document
---

@@

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Applied Social Sciences",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor")

@@

```{r exclusion2, eval=TRUE}
exclusions.2 <- c(
    "Eugenics and Social Welfare Bulletin",
    "Eugenics & Social Welfare Bull.",
    "Issues in Social Work Education", 
    "Hospital Social Service",  #Confirmed nursing journal
    "International Conference of Social Work",
    "Journal of Multicultural Social Work",
    "Journal of Social Work Process",
    "Journal of Teaching in Social Work", 
    "Maatskaplike Werk/Social Work",
    "Medical Social Work",
    "New York State Department of Social Welfare, Division Publication",
    "Pediatric Social Work", 
    "Pennsylvania Social Work",
    "Proceedings of the National Conference of Social Work","Social Service",    
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Service Monographs",
    "School Social Work Quarterly", 
    "Social Work Today",
    "Social Work Technique",
    "Social Work Today", 
    "Social Work Yearbook",
    "The New Social Worker",
    "Pennsylvania Social Work",
    "University of Chicago Social Service Monograph" 
    )

@@

```{r titleMerge, eval=TRUE}
full.df$record <- ifelse(full.df$record == 
        "The British Journal of Social Work",       # Old title
        "British Journal of Social Work",           # New title
                        full.df$record)

@@

full.df$record <- ifelse(full.df$record == "Journal of Independent Social Work" | full.df$record == "Journal of Analytic Social Work", "Psychoanalytic Social Work", 
                full.df$record)
```

@@

print.data.frame(final.list, row.names=FALSE)

@@

```{r comment=NA, echo=FALSE} 
number.of.articles <- length(which(full.df$attributes == "article"))
range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
```

@@

>>>>

---
title: "History of Social Work Research"
author: "Summary of Data Cleaning Procedures"
output: pdf_document
---

@@

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor")

@@

```{r exclusion2, eval=TRUE}
exclusions.2 <- c(
    "Eugenics and Social Welfare Bulletin",
    "Eugenics & Social Welfare Bull.",
    "Issues in Social Work Education", 
    "Hospital Social Service",  #Confirmed nursing journal
    "International Conference of Social Work",
    "Journal of Multicultural Social Work",
    "Journal of Social Work Process",
    "Journal of Teaching in Social Work", 
    "Maatskaplike Werk/Social Work",
    "Medical Social Work",
    "New York State Department of Social Welfare, Division Publication",
    "Pediatric Social Work", 
    "Pennsylvania Social Work",
    "Proceedings of the National Conference of Social Work","Social Service",    
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Service Monographs",
    "School Social Work Quarterly", 
    "Social Work Today",
    "Social Work Technique",
    "Social Work Today", 
    "Social Work Yearbook",
    "Pennsylvania Social Work",
    "University of Chicago Social Service Monograph" 
    )

@@

```{r titleMerge, eval=TRUE}
full.df$record <- ifelse(full.df$record == 
        "The British Journal of Pyschiatric Social Work",       # Old title
        "British Journal of Social Work",           # New title
                        full.df$record)

@@

full.df$record <- ifelse(full.df$record == "Journal of Independent Social Work" | full.df$record == "Journal of Analytic Social Work", "Psychoanalytic Social Work", 
                full.df$record)

# Journals were originally merged after suffixes were eliminated (after the colon).  Thus, Practice: Social Work in Action  (new title) was shortened to Practice (old title).  This section resolves two of these issues to be consistent in the comparison with Hodge.

practice.temp <- grep("^Practice$", full.df$record)
full.df$record[practice.temp] <- "Practice: Social Work in Action"

practice.temp <- grep("^Reflections$", full.df$record)
full.df$record[practice.temp] <- "Reflections: Narratives of Professional Helping"
```

@@

print.data.frame(final.list, row.names=FALSE)
```

## Intersection, Differences and Union

This section examines the overall _coverage_ of the current search by making systematic comparisons with Hodge (2013).  The first analysis shows how the list of SWH overlaps with HL -- that is, the journals that were common to both lists (_intersection_).  The sedond analyses shows the set _differences_.  The third analysis focuses on the union of the sets.  The union shows a meta-list by 
```{r}

unique.swHistory <- filter(full.df, attributes == "journal") %>%
                distinct(record)

hodge.swHistory.intersect <- intersect(hodge, unique.swHistory$record)

hodge.swHistory.diff <- setdiff(hodge, unique.swHistory$record)
swHistory.hodge.diff <- setdiff(unique.swHistory$record, hodge)

hodge.swHistory.union <- union(hodge, unique.swHistory$record)

print(sort(hodge.swHistory.intersect))
print(sort(hodge.swHistory.diff))
print(sort(swHistory.hodge.diff))
print(sort(hodge.swHistory.union))

@@

@@

Reflections: Narratives of Professional Helping
